---
title: "Transform dataset"
date: "`r Sys.Date()`"
bibliography: references.bib
biblio-style: apalike
---

## About

### Description

This script updates the CSV files created in the 'Acquire Data' section to include information regarding the state and Census Burea region of origin for each tweet.

### Usage

Within the "updated_plurals <- left_join(join_tweets_to_states(plurals),census_regions)" line of code, replace "updated_plurals" and "plurals" with the name of your updated CSV and the original CSV, respectively. Do this for each group of terms analyzed.

## Setup

```{r setup}
# Script-specific options or packages
# None are necessary in this part of the project
```

## Run

### Second Person Plurals

```{r update-plurals}
updated_plurals <- left_join(join_tweets_to_states(plurals),census_regions) # adds census regions to the plurals CSV
```

### Outdoor Sales

```{r update-sales}
updated_sales <- left_join(join_tweets_to_states(sale),census_regions) # adds census regions to the plurals CSV
```

### Gym Shoes

```{r update-shoes}
updated_shoes <- left_join(join_tweets_to_states(shoes),census_regions) # adds census regions to the plurals CSV
```

### Soft Drinks

```{r update-tonix}
updated_tonix <- left_join(join_tweets_to_states(tonix),census_regions) # adds census regions to the plurals CSV
```

### Major Roads

```{r update-roads}
updated_roads <- left_join(join_tweets_to_states(roads),census_regions) # adds census regions to the plurals CSV
```

## Finalize

### Log

If everything runs as it should, there should be no output from this code.

## References

  Vaux, Bert. “Harvard Dialect Survey.” Harvard Dialect Survey, 2003, http://dialect.redlog.net.
