---
title: "Transform dataset"
date: "`r Sys.Date()`"
bibliography: references.bib
biblio-style: apalike
---

## About

### Description

This script updates the CSV files created in the 'Acquire Data' section to include information regarding the state and Census Burea region of origin for each tweet.

### Usage

Within the "updated_plurals <- left_join(join_tweets_to_states(plurals),census_regions)" line of code, replace "updated_plurals" and "plurals" with the name of your updated CSV and the original CSV, respectively. Do this for each group of terms analyzed.

## Setup

```{r setup}
# Script-specific options or packages
library(tidyverse)

join_tweets_to_states <- function(tweets) {
  # Function
  # Takes a data frame result from an rtweet::search_term() query
  # and maps the tweets with lat/lng values to US states
  # 
  # Requires a US Census API Key: https://api.census.gov/data/key_signup.html
  # that is added to the .Renviron file with tidycensus::census_api_key()
  
  library(tidyverse, quietly = TRUE) # data manipulation
  library(tidycensus)                # us state geometries
  
  # Get the spatial geometries for each US state/ territory
  states_sf <- 
    get_acs(geography = "state", # states
            variables = "B01003_001", # total population
            geometry = TRUE) %>% # spatial geometry
    select(state_name = NAME, geometry) # only keep state name and geometry columns
  
  # Align the CRS for tweets to the census
  tweets_sf <- 
    tweets %>% # original data frame
    filter(lat != "") %>% # only keep tweets with lat/lng values
    st_as_sf(coords = c("lng", "lat"), # map x/long, y/lat values to coords
             crs = st_crs(states_sf)) # align coordinate reference system
  
  # Map tweet coords to census state geometries
  tweets_states_sf <- 
    st_join(tweets_sf, states_sf) 
  
  tweets_states_df <- 
    tweets_states_sf %>% # spatial features object
    as_tibble() %>% # convert to tibble (remove spatial features)
    filter(state_name != "") # keep only US states/ territories
  
  return(tweets_states_df) # return the final data frame
  
}
```

## Run

```{r read-census-regions}
census_regions <- read_csv(file = "../data/original/twitter/census_regions.csv")
```


### Second Person Plurals

```{r update-plurals}
updated_plurals <- left_join(join_tweets_to_states(plurals),census_regions) # adds census regions to the plurals CSV
write_csv(updated_plurals, file = "../data/derived/updated_plurals.csv") # write to disk
```

### Outdoor Sales

```{r update-sales}
updated_sales <- left_join(join_tweets_to_states(sale),census_regions) # adds census regions to the plurals CSV
write_csv(updated_sales, file = "../data/derived/updated_sales.csv") # write to disk
```

### Gym Shoes

```{r update-shoes}
updated_shoes <- left_join(join_tweets_to_states(shoes),census_regions) # adds census regions to the plurals CSV
write_csv(updated_shoes, file = "../data/derived/updated_shoes.csv") # write to disk
```

### Soft Drinks

```{r update-tonix}
updated_tonix <- left_join(join_tweets_to_states(tonix),census_regions) # adds census regions to the plurals CSV
write_csv(updated_tonix, file = "../data/derived/updated_tonix.csv") # write to disk
```

### Major Roads

```{r update-roads}
updated_roads <- left_join(join_tweets_to_states(roads),census_regions) # adds census regions to the plurals CSV
write_csv(updated_roads, file = "../data/derived/updated_roads.csv") # write to disk
```

## Finalize

### Log

If everything runs as it should, there should be no output from this code.

## References

  Vaux, Bert. “Harvard Dialect Survey.” Harvard Dialect Survey, 2003, http://dialect.redlog.net.
