---
title: "Project Title"
date: "`r Sys.Date()`"
bibliography: references.bib
biblio-style: apalike
---

## Project title

<!-- Add overview of the project here. -->

### Research area and problem

The research area for this project will be dialectology, and the ability of API-based corpora to capture elements of regional dialect variation.

The uncertainty surrounding typed-language's ability to capture distinctive, regional aspects of language use.

### Research aim and question

To compare the findings of API-based data to more traditionally compiled corpora, and discover whether attributes of regional dialects are noticeable in language used on Twitter.

Are established aspects of regional dialects found in API-based data, such as tweets? To what extent are dialects discernible in typed language?

## Reproduce

### Session

<details>

<summary>

View session information

</summary>

```{r}
sessioninfo::session_info()
```

</details>

```{r cleanup, echo=FALSE}
rm(list = ls()) # clean working environment
```

## References

[@clopper2006; @grieve2019; @moisl; @nguyen2017; @yumpu.com; @zaghouani2018; @szmrecsanyi2011]
